Data Preparation, Integration and Cleaning

### 2018-05-21 scripts/3_data_prep.Rmd
Start re-write of data analysis script
Bug fix: ;geo_mrkt definition error

   # Add individual classes
   str_sf$geo_mrkt <- 'rural'
   str_sf$geo_mrkt[str_tdf$sub_des == 'Middle'] <- 'suburban'
   str_sf$geo_mrkt[str_tdf$sub_des == 'Inner'] <- 'city'
   str_sf$geo_mrkt[str_tdf$suburb %in% core_suburbs] <- 'city-core'
   str_sf$geo_mrkt[str_tdf$beach == 1] <- 'beach'

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        file=paste0(data_path, '/prepared/prepared_data.RData'))

>>>>

   # Add individual classes
   str_sf$geo_mrkt <- 'rural'
   str_sf$geo_mrkt[str_sf$sub_des == 'Middle'] <- 'suburban'
   str_sf$geo_mrkt[str_sf$sub_des == 'Inner'] <- 'city'
   str_sf$geo_mrkt[str_sf$suburb %in% core_suburbs] <- 'city-core'
   str_sf$geo_mrkt[str_sf$beach == 1] <- 'beach'

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))
